---
title: "Tutorial Title"
author: "Author"  
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Git.. GitHub.. What are they? Why do they matter? This tutorial will introduce you to Git and GitHub. This presentation is for individuals with limited knowledge on Git and GitHub, although those with robust knowledge or background are more than welcome to join!  

#### Learning objectives
- Develop an understanding of what Git and GitHub are 
- Install Git, GitHub and RStudio
- Connect Git, GitHub and RStudio

## Git
#### What is Git
Have you ever tried working on a project or a specific piece of code with another teammate? Or have you ever overwritten your own code and had to rewrite the chunk from the beginning?

Frustrating, right? Well, Git is software that allows you to do better. Be a better coder, communicator and even a better loved one because the time you will save can be used elsewhere. 

Now, I will preface by saying that there is a learning curve to Git. But keep at it, take breaks, and do not ignore your mental health.

#### Setup
Let's get started shall we!

Setting up a token in RStudio
usethis::create_github_token()
gitcreds::gitcreds_set()


## GitHub
#### What is GitHub
#### Setup
#### Repositories


## RStudio
#### Setup

#Checking Your Current Version of R 
R.version.string

# --------- Introducing Yourself to Git ---------
#install if needed (do this exactly once):
#install.packages("usethis")

library(usethis)
use_git_config(user.name = "Michelle Slawinski", user.email = "slawinsm@gmail.com")
```

## Examples

Examples are key to meeting your learning objectives. Consider your audience, learning objectives, and narrative when writing examples (see [The Carpentries Curriculum Development](https://carpentries.github.io/curriculum-development/) for tips). The learner needs to be able to reproduce examples from your tutorial on their computer. To do this, we look to advice on how to create a [minimal, reproducible example](https://stackoverflow.com/a/5963610). Examples may include:

- Problem or goal
- Dataset
- Solution code
- Information for reproducibility

## Dataset

Almost all examples require an input. That is what is meant by "dataset". You can create your own dataset or use one that is built into R.

**Create-your-own:**

Known values
```{r}
x <- c(1, 5, 9, 10)
```

Random values (set seed to make it reproducible)
```{r}
set.seed(20)
y <- rnorm(4)
```
See guidance on [minimal, reproducible example](https://stackoverflow.com/a/5963610) for more examples.

**Built-in:**

Available datasets in R (run in RStudio to see list)
```{r}
data() 
```

A popular example dataset is 'iris'
```{r}
head(iris)
```

Another great example dataset is 'penguins'
```{r}
# install the package if it's not already installed
if(!("palmerpenguins" %in% installed.packages()[,"Package"]))
  install.packages("palmerpenguins")

# load package
library(palmerpenguins)

# show data
head(penguins)
```


## Solution code

We will use an example from the [palmerpenguins vignette](https://allisonhorst.github.io/palmerpenguins/articles/intro.html) to demonstrate solution code. For this example, the goal is to create a scatterplot for data with different categories.

**Install packages if they're not already installed** 

This handy code is from [Stackoverflow](https://stackoverflow.com/a/4090208). List the packages a learner would need for your tutorial in the first line.
```{r}
list.of.packages <- c("palmerpenguins", "dplyr", "ggplot2")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
```

**Load packages** 

We use the code chunk option "message = F" to suppress messages generated when packages load.
```{r, message = F}
library(palmerpenguins)
library(dplyr)
library(ggplot2)
```

**Settings**

Include figure settings, saved variables, and create-your-own datasets.
```{r}
theme_set(theme_minimal())
```

**Solution**

Code to create scatterplot. We use the option out.width to make the figure clearer and smaller.
```{r, out.width = "50%"}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species,
                 shape = species),
             size = 2) +
  scale_color_manual(values = c("darkorange","darkorchid","cyan4"))
```

If there are variations on your solution, provide more examples!


## Information for reproducibility

R and R packages are continuously updated and examples that work under a certain set of conditions may not work under another set. Ideally, you would update your tutorial when key software is updated to maintain working examples. However, that may not be feasible, and the next best option is to provide learners with all the necessary information about your computing environment. This can help them identify differences with their computing environment that may be preventing the example from running as expected. 

**My computing environment:**

Session information
```{r}
sessionInfo()
```

RStudio version
```{r}
rstudioapi::versionInfo()$version
```


## Sharing your tutorial

### Slides
If you're sharing your tutorial at an R-Ladies meeting, consider making slides to go along with it.

See the [R-Ladies Gainesville presentations repository](https://github.com/R-Ladies-Gainesville/presentations) to download the the R Markdown file `tutorial_template.Rmd`. The tutorial_template presentation is created with the [xaringan](https://slides.yihui.org/xaringan/#1) package and the RLadies theme by [Alison Hill](https://www.apreshill.com/project/rladies-xaringan/).

### Github

Now it's time to add your tutorial to the R-Ladies Gainesville [tutorials repository](https://github.com/R-Ladies-Gainesville/tutorials). This will make it easier for others to provide feedback and for people to use your tutorial!

If you do not use Github, email your `.Rmd` file to R-Ladies Gainesville at <gainesville@rladies.org>.
